---
title: Exercises 1. Vectors 
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Question 1a
```{r}
H <- (1:20)
H
```
Question 1b
```{r}
X <- (20:1)
X
```
Question 1c
```{r}
F <- c(1:20,19:1)
F
```
Question 1d
```{r}
P <- c(4,6,3)
```
Question 1e
```{r}
rep(c(4,6,3) , times = 4)
```
Question 1f
```{r}
rep(c(4,6,3),times = c(10,1,1))
```
Question 1g
```{r}
rep(c(4,6,3), times = c(11,10,10))
```
Question 1h
```{r}
rep(c(4,6,3), times = c(10,20,30))
```
Question 2
```{r}
x <- seq(3 ,6, 0.1)
x
exp(x)*cos(x)
```
Question 3a
```{r}
x <- seq(3,36 ,by =3)
y <- seq(1,34 ,by =3)
z <- rep(0.1, times = 12)
h <- rep(0.2, times = 12)
g <- z^x*h^y
g
```
Question 3b
```{r}
x <- seq(2,25)
y <- 2
z <- c(y,y^x/x)
z
```
Question 4a
```{r}
H =c(10:100)
sum(H + 4^2)
```   
Question 4b
```{r}
H <- c(1:25)
sum(2^H/H + 3^H/H^2)
```
Question 5a
```{r}
x <- paste("label",1:30)
x
```
Question 5b
```{r}
x <- paste0("fn",1:30)
x
```
Question 6a
```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
z <- yVec[seq(2:250)]-xVec[seq(1:249)]
z
```
Question 6b 
```{r}
sinyVec <- sin(yVec)
CosxVec <- cos(xVec)
R <- sinyVec/CosxVec
R
```
Question 6c
```{r}
y <- xVec[1:248]
m <- xVec[2:249]
w <- xVec[3:250]
ZY <- y + 2 * m - w
ZY
```
Question 6d
```{r}
x <- xVec[-length(xVec)]+10
y <- exp(-xVec[-1])
z <- sum(y/x)
z
```
Question 7a
```{r}
X <- sort(yVec[1:600])
X
```
Question 7b
```{r}
x <- which(yVec >600)
x
```
Question 7c
```{r}
x <- which(xVec > 600)
y <- which(yVec > 600)
x <- append(x,y,after = length(x))
h <- sort(x)
h
h[duplicated(h)]

```
Question 7d
```{r}
G <- abs(xVec - mean(xVec))
sqrt(G)
```
Question 7e
```{r}
R <- sum( yVec>max(yVec)-200 )
R

```
Question 7f
```{r}
xVec[which(xVec %% 2 == 0)]
```
Question 7g
```{r}
sort(order(xVec)[yVec]) 
```
Question 7h
```{r}
yVec[seq(1,250, by=3)]
```
Question 8
```{r}
d <- seq(2,38,by=2)
e <- seq(3,39,by=2)
T <- sum(cumprod(d/e))
1 + T
```

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
